TODO

### 2024-04-08 paper/paper.qmd
made model tables

---
title: "TODO"
subtitle: "TODO"
author: 
  - Shivank Goel
thanks: "Code and data are available at: https://github.com/shivankgoel003/DataBreach_Ransomware_Stats"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
header-includes:
   - \usepackage{tikz}
   - \usetikzlibrary{shapes.geometric, arrows.meta, positioning, fit, calc}
   - \usepackage{pgfplots} 
   - \usepackage{float}
format: pdf
number-sections: true
bibliography: references.bib
---

@@

[@tbl-modelbreachseverity] summarises the results from model.

@@

R-squared (0.137): Indicates the proportion of variance in the dependent variable that's predictable from the independent variables. A value of 0.137 suggests the model explains about 13.7% of the variability in breach severity.

Adjusted R-squared (0.099): It adjusts the R-squared for the number of predictors in the model. It is lower than the R-squared, which is common in models with many predictors.

AIC (665.5) and BIC (746.7): These are measures for model comparison.

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| label: tbl-modelbreachseverity
#| tbl-cap: "Linear Regression Model Summary for RQ1"
#| message: false
#| 
library(modelsummary)

breach_severity_model <- readRDS(file = here::here("models/breach_severity_model.rds"))

modelsummary(list("Linear Regression" = breach_severity_model))

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
#| 
library(modelsummary)

logistic_model <- readRDS(file = here::here("models/restructuring_model.rds"))

modelsummary(list("Logistic Regression" = logistic_model))

@@

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false
# Summary statistics for numerical variables
summary(breach_data$number_of_users_affected)
summary(breach_data$year)

# Frequency tables for categorical variables
table(breach_data$sector)
table(breach_data$organisation_size)
table(breach_data$critical_industry)
table(breach_data$level_of_digital_intensity)
table(breach_data$country)
table(breach_data$cyber_security_role)
table(breach_data$cyber_security_frameworks)
table(breach_data$education_and_awareness_policy)
table(breach_data$policy)
table(breach_data$prevention_detection_and_recovery)
table(breach_data$detector)
table(breach_data$restructuring_after_attack)
table(breach_data$bribe_ransom_paid)
table(breach_data$free_identity_or_credit_theft_monitoring)
table(breach_data$additional_disclosure_of_information)
table(breach_data$overall_nature_of_attack)
table(breach_data$attack_type)
table(breach_data$attacker)
table(breach_data$attack_vector)
table(breach_data$impact_on_data)
# ... continue for other categorical variables as needed

# Histogram for a continuous variable (e.g., number_of_users_affected)
ggplot(breach_data, aes(x = number_of_users_affected)) +
  geom_histogram(binwidth = 1000, fill = "blue", color = "black") +
  labs(title = "Histogram of Number of Users Affected", x = "Number of Users Affected", y = "Frequency")

>>>>

---
title: "TODO"
subtitle: "TODO"
author: 
  - Shivank Goel
thanks: "Code and data are available at: https://github.com/shivankgoel003/DataBreach_Ransomware_Stats"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
header-includes:
   - \usepackage{tikz}
   - \usetikzlibrary{shapes.geometric, arrows.meta, positioning, fit, calc}
   - \usepackage{pgfplots} 
   - \usepackage{float}
   - \usepackage{booktabs}
   - \usepackage{longtable}

format: pdf
number-sections: true
bibliography: references.bib
---

@@

[@breach_severity_model] summaries the results from model.

@@

R-squared (0.137): Indicates the proportion of variance in the dependent variable that's predictable from the independent variables. A value of 0.137 suggests that approximately 13.71% of the variation in breach severity is explained by the included predictors.

Adjusted R-squared (0.099): This value is slightly lower than the R-squared, and accounts for the number of predictors,. It suggests a good fit of the model considering the complexity introduced by multiple variables.

F-statistic of 3.619 and a p-value of 1.12e-06, suggests that the model demonstrates the statistical significance overall, indicating that at least some of the predictors are likely to be genuinely associated with variations in breach severity.

\begin{longtable}{lcccc}
\caption{Linear regression analysis with breach severity numeric as dependent variable} \label{tab:breach_severity_model} \\
\toprule
Predictor & Estimate & Std. Error & t value & Pr(>|t|) \\
\midrule
\endfirsthead

\multicolumn{5}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\toprule
Predictor & Estimate & Std. Error & t value & Pr(>|t|) \\
\midrule
\endhead

\midrule \multicolumn{5}{r}{\textit{Continued on next page}} \\
\endfoot

\endlastfoot

Intercept & 2.08715 & 0.09139 & 22.837 & $<$ 2e-16 *** \\
Organisation Size - Medium & 0.01467 & 0.08055 & 0.182 & 0.855 \\
Organisation Size - Small & 0.10336 & 0.10093 & 1.024 & 0.306 \\
Organisation Size - Unknown & -0.07151 & 0.07166 & -0.998 & 0.319 \\
Level of Digital Intensity - Low & -0.29052 & 0.22750 & -1.277 & 0.202 \\
Level of Digital Intensity - Low-Medium & 0.11865 & 0.16894 & 0.702 & 0.483 \\
Level of Digital Intensity - Medium-High & 0.45764 & 0.15186 & 3.013 & 0.0027 ** \\
Sector - Public Administration and Defence & -0.58112 & 0.20077 & -2.894 & 0.0040 ** \\
Sector - Other & -0.44159 & 0.12026 & -3.672 & 0.0003 *** \\
Sector - Arts, Entertainment and Recreation & -0.80423 & 0.20009 & -4.019 & 6.94e-05 *** \\
Sector - Education & -0.27055 & 0.20130 & -1.344 & 0.180 \\
Sector - Human Health Activities & -0.20620 & 0.19467 & -1.059 & 0.290 \\
Country - Canada & -0.55895 & 0.30172 & -1.853 & 0.0646 . \\
Country - Global & -0.41952 & 0.16428 & -2.554 & 0.0110 * \\
Country - Japan & -0.21109 & 0.26805 & -0.788 & 0.431 \\
Country - UK & 0.07899 & 0.30459 & 0.259 & 0.795 \\
Country - Other & 0.13767 & 0.15593 & 0.883 & 0.378 \\
Country - Singapore & -0.68348 & 0.30035 & -2.276 & 0.0234 * \\
Country - South Korea & -0.74056 & 0.52226 & -1.418 & 0.157 \\
\midrule
Residual standard error & \multicolumn{4}{c}{0.5131 on 410 DF} \\
Multiple R-squared & \multicolumn{4}{c}{0.1371} \\
Adjusted R-squared & \multicolumn{4}{c}{0.09921} \\
F-statistic & \multicolumn{4}{c}{3.619 on 18 and 410 DF} \\
P-value & \multicolumn{4}{c}{1.12e-06} \\
\bottomrule
\end{longtable}

@@

\begin{longtable}{lrrrr}
\caption{Linear regression analysis with number of users affected as dependent variable} \label{tab:my_label} \\
\toprule
Model & Coefficients & Standard errors & T value & Sig \\
\midrule
\endfirsthead

\multicolumn{5}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\toprule
Model & Coefficients & Standard errors & T value & Sig \\
\midrule
\endhead

\midrule \multicolumn{5}{r}{\textit{Continued on next page}} \\
\endfoot

\endlastfoot

Intercept & 36,687,660 & 32,842,060 & 1.117 & 0.264 \\
Cyber Security Role & NA & NA & NA & NA \\
Cyber Security Frameworks & -13,994,198 & 139,505,210 & -0.100 & 0.920 \\
Education and Awareness Policy & 38,460,000 & 194,290,149 & 0.198 & 0.843 \\
Prevention, Detection, and Recovery & NA & NA & NA & NA \\
Organization Size - Medium & -7,347,889 & 29,571,997 & -0.248 & 0.804 \\
Organization Size - Large & 8,946,092 & 25,705,975 & 0.348 & 0.728 \\
Organization Size - Unknown & -14,379,354 & 28,602,186 & -0.503 & 0.615 \\
Sector - Public Administration and Defence & 81,232,193 & 41,730,689 & 1.947 & 0.052 \\
Sector - Other & 73,186,958 & 25,457,748 & 2.875 & 0.004 \\
Sector - Arts, Entertainment and Recreation & 93,277,310 & 41,274,076 & 2.260 & 0.024 \\
Sector - Education & 40,468,643 & 31,559,658 & 1.282 & 0.200 \\
Sector - Human Health Activities & 47,359,281 & 28,602,617 & 1.656 & 0.098 \\
Level of Digital Intensity & -28,344,216 & 9,431,846 & -3.005 & 0.003 \\
\midrule
R Squared & \multicolumn{4}{c}{0.093} \\
Adjusted R Squared & \multicolumn{4}{c}{0.037} \\
F Statistic & \multicolumn{4}{c}{1.648} \\
Significance of F & \multicolumn{4}{c}{0.018} \\
\bottomrule
\end{longtable}
```

@@

```{r}
# Histogram for a continuous variable (e.g., number_of_users_affected)
ggplot(breach_data, aes(x = number_of_users_affected)) +
  geom_histogram(binwidth = 1000, fill = "blue", color = "black") +
  labs(title = "Histogram of Number of Users Affected", x = "Number of Users Affected", y = "Frequency")
